Insert the article title here

### 2018-08-20 writeup/manuscript.tex
bug s due to changed column names. need fixed
Added new figures from Jess

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-foragers' showed no switch cost. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that test-retest reliability is <INSERT DETAILS>

@@

In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a $10 \times 8$ grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized.

For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun. In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

@@

Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors. When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial N was different to the colour chosen on trial N-1).

The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018} (see Figure \ref{fig:acvs_summary}). shows that there were wide individual differences in both percent option (range $33.62\%$ - $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_OptCh_x_SwRate.png}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_groupplot.pdf}}
\caption{Needs checked and updated. replace png with pdf!}
\label{fig:acvs_summary}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../Scripts/foraging/FG_IndivDiffsFig.png}
\caption{What do we want this figure to actually be?}
\label{fig:foraging_summary}
\end{figure*}

@@

>>>>

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-foragers' showed no switch cost. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that the test-retest reliability is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.

@@

In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a $10 \times 8$ grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized. For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun. In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

@@

Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors. When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial $N$ was different to the colour chosen on trial $N-1$).

The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018}. We can clearly see from figure \ref{fig:acvs_summary} that there are individual differences in both the proportion of optimal targets reported (range $33.62\%$ - $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).

\begin{figure}
\centering
\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}}
\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_switchRate_hist.pdf}}
\caption{Histograms showing the range of individual differences found in the ACVS task.}
\label{fig:acvs_summary}
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_featureRunLength_hist.pdf}}
\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}}
\caption{What do we want this figure to actually be?}
\label{fig:foraging_summary}
\end{figure}

@@

The feature search condition from the MCFT will be discarded from this analysis, as the individual differences of interest relate to how people search in the conjunction condition. Measures for the SHLS task will be taken from
